% #############################################################################
% Agradecimentos / Acknowledgments
% !TEX root = ../main.tex
% #############################################################################

The first appreciations go to my thesis supervisors, Prof. António Grilo and Prof. João Carvalho, due to all the precious guidance, help and advice provided.

I would also like to thank Eng. Sandra Mesquita for the availability and the important informations supplied, CCDR-LVT stations maintenance employees for the collaboration in the placement of the developed sensors in the monitoring stations.
I would also like to extend my thanks to Eng. Luís Lamela from Altice Portugal and Eng. Jose Adarve from Quectel, for the provided debugging help with the new NB-IoT devices, and Altice Golabs.IoT Laboratory for the given opportunity to learn about new IoT technologies in their workshops.

To all my good and remarkable friends Francisco Fialho, Celso Mateus, Raquel Baptista, Filipa Lindo, Maria Belo, Carlos Carvalho, Rodrigo Jacinto, Sara Valente, Carla Vicente, Luís Bucho, Filipa Ribeiro, João Filipe, Magali Correia, and to all that were not mentioned, for their long and lasting friendships and for all the support given during these years.

I would like to express my deep gratitude to NEECIST for all the experiences, friendships and knowledge provided during my college life.

To all my family, most notably to my mother, Adélia Amaral, my father, Pedro Amaral, my brother, Francisco Amaral, my aunt and my godfather, Madalena Bernardo and Manuel Bernardo, and to the rest of my family, for their unconditional daily support and patience.

Finally to my loved one and best friend, Mónica Lourenço, for all her love, care and support.
